\vskip-0.6in \Large Political Uncertainty

### 2015-05-16 GS-extension.tex
add section headings / toc to GS-extension
add 2nd derivative w.r.t. Z for SOC
add cross-partial for SOC

On Feb. 12, Sebastian and I agreed to focus efforts on finding a base model to facilitate empirical identification. I am pursuing Groseclose $\&$ Snyder (1996), ``Buying Supermajorities,'' APSR
\begin{itemize}
	\item For each legislator $i$, $v(i) = u_i(x) - u_i(s)$, measured in money; this is the reservation price of $i$
		\begin{itemize}
			\item $x$ is an alternative policy proposal; $s$ is the status quo
			\item WLOG, label legislators so that $v(i)$ is a non-increasing function 
			\item Note legislators only have preferences over how they vote, not over which alternative wins
		\end{itemize}
	\item There are two vote buyers; each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP
		\begin{itemize}
			\item $A$ prefers $x$; $W_A$ is $A$'s willingness to pay (WTP) for $x$ measured in money
			\item $B$ prefers $s$; $W_B$ is $B$'s WTP for $s$
		\end{itemize}
	\item Bribe offer functions: $a(i)$ and $b(i)$ are $A$ and $B$'s offers to $i$. Legislators take these bribe offers as given and then vote for the alternative that maximizes their payoff
	\item A moves first; $a(i)$ is perfectly observable to $B$ when he moves
	\item Goal: characterize SPNE in pure strategies
		\begin{itemize}
			\item Assume unbribed legislators who are indifferent vote for $s$; all bribed legislators who are indifferent vote for whoever bribed them last
		\end{itemize}
	\item Assume continuum of legislators on $\left[-\frac{1}{2},\frac{1}{2}\right]$
	\item Assume $W_A$ large enough that $x$ wins in equilibrium (no uncertainty case)
	\item $m + \frac{1}{2}$ is fraction of legislators who vote for $x$ as opposed to the status quo, $s$
	\item Results
	\begin{itemize}
		\item Prop 1: three types of equilibria in which $x$ wins; depend on size of $W_B$
		\item Prop 2: $m^*$ (the optimal coalition size) is unique, and provides three cases parameterizing its size in terms of $W_B$, $v(-\frac{1}{2})$ and $v(m^*)$
		\item Prop 3/4: special case where $v(z) = \alpha - \beta z$
	\end{itemize}
\end{itemize}

\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

@@

\newpage
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]
		\[
		  e^{-X} = e^{-Y-Z}
		\]
		\begin{equation}
		  -X = -Y-Z
			\label{eq:X}
		\end{equation}
		By symmetry, we also have
		\begin{equation}
		  -Y = -X - Z
			\label{eq:Y}
		\end{equation}
		\begin{equation}
		  -Z = -X - Y
			\label{eq:Z}
		\end{equation}
		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
		\[
		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
		\]
		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
		\[
		  X = Y = Z = 0
		\]		
\end{itemize}

\vskip1in
Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page). The first derivative of the objective function w.r.t. $b(-\frac{1}{2})$ is (in logistic form)
\[
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
\]
\[
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
\]
Now, the second derivative:
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
\]
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$. So this objective function appears to have an inflection point at $z=0$.

\newpage
Comparative statics
\begin{itemize}
	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
		\begin{itemize}
			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
				\[
					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
				\]
			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
				\[
				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
				\[
				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
		\end{itemize}
\end{itemize}

\newpage
Notes from 3/16 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
\end{itemize}

>>>>

\section{Groseclose and Snyder 1996}
On Feb. 12, Sebastian and I agreed to focus efforts on finding a base model to facilitate empirical identification. I am pursuing Groseclose $\&$ Snyder (1996), ``Buying Supermajorities,'' APSR
\begin{itemize}
	\item For each legislator $i$, $v(i) = u_i(x) - u_i(s)$, measured in money; this is the reservation price of $i$
		\begin{itemize}
			\item $x$ is an alternative policy proposal; $s$ is the status quo
			\item WLOG, label legislators so that $v(i)$ is a non-increasing function 
			\item Note legislators only have preferences over how they vote, not over which alternative wins
		\end{itemize}
	\item There are two vote buyers; each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP
		\begin{itemize}
			\item $A$ prefers $x$; $W_A$ is $A$'s willingness to pay (WTP) for $x$ measured in money
			\item $B$ prefers $s$; $W_B$ is $B$'s WTP for $s$
		\end{itemize}
	\item Bribe offer functions: $a(i)$ and $b(i)$ are $A$ and $B$'s offers to $i$. Legislators take these bribe offers as given and then vote for the alternative that maximizes their payoff
	\item A moves first; $a(i)$ is perfectly observable to $B$ when he moves
	\item Goal: characterize SPNE in pure strategies
		\begin{itemize}
			\item Assume unbribed legislators who are indifferent vote for $s$; all bribed legislators who are indifferent vote for whoever bribed them last
		\end{itemize}
	\item Assume continuum of legislators on $\left[-\frac{1}{2},\frac{1}{2}\right]$
	\item Assume $W_A$ large enough that $x$ wins in equilibrium (no uncertainty case)
	\item $m + \frac{1}{2}$ is fraction of legislators who vote for $x$ as opposed to the status quo, $s$
	\item Results
	\begin{itemize}
		\item Prop 1: three types of equilibria in which $x$ wins; depend on size of $W_B$
		\item Prop 2: $m^*$ (the optimal coalition size) is unique, and provides three cases parameterizing its size in terms of $W_B$, $v(-\frac{1}{2})$ and $v(m^*)$
		\item Prop 3/4: special case where $v(z) = \alpha - \beta z$
	\end{itemize}
\end{itemize}

\section{Our Extension to Uncertainty}
\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

\subsection{Solving the Model}

@@

\section{Discrete Model}

@@

\subsection{Math for Discrete Model}
\newpage
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]
		\[
		  e^{-X} = e^{-Y-Z}
		\]
		\begin{equation}
		  -X = -Y-Z
			\label{eq:X}
		\end{equation}
		By symmetry, we also have
		\begin{equation}
		  -Y = -X - Z
			\label{eq:Y}
		\end{equation}
		\begin{equation}
		  -Z = -X - Y
			\label{eq:Z}
		\end{equation}
		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
		\[
		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
		\]
		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
		\[
		  X = Y = Z = 0
		\]		
\end{itemize}

\subsection{Second Order Condition}
Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page). The first derivative of the objective function w.r.t. $b(-\frac{1}{2})$ is (in logistic form)
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
\end{equation}
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
	\label{eq:firstderiv}
\end{equation}
Now, the second derivative:
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
\]
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$. So this objective function appears to have an inflection point at $z=0$.
\begin{itemize}
	\item When $z < 0$ (as when this legislator is naturally against you and you don't bribe her), this expression is negative
\end{itemize}

\vskip1in
We also need cross partials. Let's start with the first derivative for $b\left(\frac{1}{2}\right)$, analogous to Expression~\ref{eq:firstderiv} for $b\left(-\frac{1}{2}\right)$:
\begin{equation}
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1
\end{equation}

Taking the derivative of this expression with respect to $b\left(0\right)$:
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)(-1)e^{-X} -\left(e^{-X}+ e^{-Z}\right)\left(-e^{-X}- e^{-X-Z}\right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(e^{-X}+ e^{-Z}\right)\left(e^{-X} + e^{-X-Z}\right) - \left(1+e^{-X}\right)\left(1+e^{-Z}\right)e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(e^{-2X} + e^{-2X-Z} + e^{-X-Z} + e^{-X-2Z}\right) - \left(1 +e^{-X} +e^{-Z}+ e^{-X-Z} \right)e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-2X} + e^{-2X-Z} + e^{-X-Z} + e^{-X-2Z} - e^{-X} - e^{-2X} - e^{-X-Z} - e^{-2X-Z}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X-2Z} - e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]
\[
  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
\]

\newpage
\section{Some Comparative Statics}			
Comparative statics
\begin{itemize}
	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
		\begin{itemize}
			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
				\[
					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
				\]
			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
				\[
				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
				\[
				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
		\end{itemize}
\end{itemize}

\section{Notes from March}
\newpage
Notes from 3/16 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
\end{itemize}
